Case for Support

### 2021-11-17 application/Je-S_sections.tex

5. Extend and support the Bonsai user community through code and forum engagement and development workshops.

@@

Understanding the brain is a major scientific challenge of our era. To succeed, scientists must be able to explain how animal behaviour relates to neural activity across different brain regions. This requires careful design and manipulation of behavioural experiments, where experimenters either record or manipulate neural activity while the animals (e.g. non-human primates, rodents, fish, insects) perform particular tasks.

>>>>

5. Extend and support the Bonsai user community through code, documentation, and forum engagement and development workshops.

@@

Understanding the brain and the behaviour it generates is a major scientific challenge of our era. To succeed, scientists must be able to explain how animal behaviour relates to neural activity across different brain regions. This requires careful design and manipulation of behavioural experiments, where experimenters either record or manipulate neural activity while the animals (e.g. non-human primates, rodents, fish, insects) engage in specific behaviours which need to be carefully observed and quantified.

### 2021-11-17 application/detailsOfResource.tex

As it stands, Bonsai is designed to be extensible and is distributed with a package-management framework that controls installation of optional core packages as well as user-contributed extensions.
%
However extensions must be written in Bonsai's native C\# programming language.
%
This specificity restricts the range of potential contributors to the ecosystem.
%
It also hinders easy incorporation of published analytic tools, many of which are implemented within other interpreted language systems such as Python, R, or MATLAB.  
\begin{wrapfigure}{R}{0pt}
  \includegraphics[width=0.5\textwidth]{figures/extensions.pdf}%
%   \input{figures/extensions}
  \caption{Proposed extensions to Bonsai}
  \label{fig:proposedBonsaiExtensions}
\end{wrapfigure}

@@

Precisely quantifying animal behaviour is an essential step toward understanding
brain function.  Deeplabcut is a Python-based software for tracking animal body
parts \citep{mathisEtAl18}, which it is currently well integrated with
Bonsai~\citep{kaneEtAl20}. Here we propose extensions to Bonsai to extract
other informative features from video recordings.

>>>>

Bonsai is designed to be extensible and is distributed with a package-management framework that controls installation of optional core packages as well as user-contributed extensions.
%
However, extensions must be written in Bonsai's native C\# programming language.
%
This restricts the range of potential contributors to the ecosystem.
%
It also hinders incorporation of published analytic tools, many of which are implemented within other interpreted language systems such as Python, R, or MATLAB.  
\begin{wrapfigure}{R}{0pt}
  \includegraphics[width=0.5\textwidth]{figures/extensions.pdf}%
%   \input{figures/extensions}
  \caption{Proposed extensions to Bonsai}
  \label{fig:proposedBonsaiExtensions}
\end{wrapfigure}

@@

Precisely quantifying animal behaviour is an essential step toward understanding
brain function.  DeepLabCut is a Python-based software for tracking animal body
parts \citep{mathisEtAl18}, which is currently well integrated with
Bonsai~\citep{kaneEtAl20}. Here we propose extensions to Bonsai to extract
other informative features from video recordings.
